### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update to report

The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known. The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations. The HRR of the fire was estimated using documentation of the potential fuel load within the structure. Although there might be differences between the actual values and those used in the simulation, the model input parameters represent our best estimate of the fire scenario based on the information that was available. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

>>>>

The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known. The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations. The HRR of the fire was estimated using documentation of the potential fuel load within the structure. According to the McCaffrey, Quintiere, and Harkleroad correlation for a typical compartment fire, a change in the hot gas layer temperature rise is proportional to a change in the HRR raised to the \sfrac{2}{3} power. Following this relationship, in a well ventilated compartment, a 7.5~\% increase in HRR would result in a 5~\% increase in temperature~\cite{NUREG_1824_Sup_1}. In reality, input variables more closely resemble distributions than fixed point values which are used as inputs into FDS. For a detailed discussion on propagation of parameter uncertainty, see NUREG-1824 Supplement 1~\cite{NUREG_1824_Sup_1}. The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
